\documentclass[12pt, a4paper]{article}
\setlength{\oddsidemargin}{0.5cm}
\setlength{\evensidemargin}{0.5cm}
\setlength{\topmargin}{-1.6cm}
\setlength{\leftmargin}{0.5cm}
\setlength{\rightmargin}{0.5cm}
\setlength{\textheight}{24.00cm} 
\setlength{\textwidth}{15.00cm}
\parindent 0pt
\parskip 5pt
\pagestyle{plain}

\title{Research Proposal}
\author{}
\date{}

\newcommand{\namelistlabel}[1]{\mbox{#1}\hfil}
\newenvironment{namelist}[1]{%1
\begin{list}{}
    {
        \let\makelabel\namelistlabel
        \settowidth{\labelwidth}{#1}
        \setlength{\leftmargin}{1.1\labelwidth}
    }
  }{%1
\end{list}}

\begin{document}
\maketitle

\begin{namelist}{xxxxxxxxxxxx}
\item[{\bf Title:}]
	identify functionality in black box systems using neural networks.
\item[{\bf Author:}]
	Johnathan DiMatteo
\item[{\bf Supervisor:}]
	Professor Sebastian Fischmeister
\item[{\bf Degree:}]
	MMath
\end{namelist}

\section*{Background} 
% In this section you should give some background to your
% research area. What is the problem you are tackling, and why is it
% worthwhile solving? Who has already done some work in this area,
% and what have they achieved?
distances - DTW, pearson

clustering algorithms - k means, dbscan, gmm

other - hmm, autoencoders

\section*{Aim} 
%Now state explicitly the hypothesis you aim to
%test. Make references to the items listed in the Reference section
%that back up your arguments for why this is a reasonable
%hypothesis to test, for example the work of Knuth~\cite{knuth}.
%Explain what you expect will be accomplished by undertaking this
%particular project.  Moreover, is it likely to have any other
%applications?

Given no a priori knowledge of an I2C black box system, how does it's behaviour change with respect to various inputs?
Given a black box system, which inputs should be used to identify behavioural anomalies?  (To select best msgs for polygraph )
How: tune a neural network through online training ie. select a subset of msgs, train cnn: (msg, state) -> trace, fuzz with those msgs (while changing state), return msgs that obtain best classification metrics

identify the acceptable input grammar. 
A novel approach to model learning using machine learning.
by sending I2C messages and analyzing the power trace with neural networks.
Uses: black box HIL testing by manufacturers, finding undocumented functionality for security purposes, input grammar for fuzz tests, inputs for polygraph

\section*{Method}
In this section you should outline how you intend to go
about accomplishing the aims you have set in the previous
section. Try to break your grand aims down into small,
achievable tasks. Try to estimate how long you will
spend on each task, and draw up a timetable for each
sub-task.

\section*{Software and Hardware Requirements}
Outline what your specific requirements will be with regard
to software and hardware, but note that any special requests
might need to be approved by your supervisor and the Head of
Department.

Overall, you should aim to produce roughly a two page document
(and certainly no more than four pages)
outlining your plan for the year.

\begin{thebibliography}{9}
\bibitem{knuth} D. E. Knuth. {\em The \TeX~book.}\/ Addison-Wesley,
Reading, Massachusetts, 1984.
\bibitem{lamport} L. Lamport. {\em \LaTeX~: A Document Preparation
System}.\/ Addison-Wesley, Reading, Massachusetts, 1986.
\bibitem{ken} Ken Wessen, Preparing a thesis using \LaTeX~, private
communication, 1994.
\bibitem{lamport2} L. Lamport. Document Production: Visual
or Logical, {\em Notices of the Amer. Maths. Soc.},\/ Vol. 34,
1987, pp. 621-624.
\end{thebibliography}


\end{document}


